---
title: "subject_by_node_Viewing1_Viewing2"
output: html_document
date: '2023-10-31'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(lme4)
library(lmerTest)
library(MASS)
library(Rcpp)
library(ggplot2)
library(tidyverse)
library(ggsignif)
library(nlme)
library(sjPlot)
library(cowplot)
library(ggside)
library(patchwork)
library(dplyr)
library(ggh4x)
library(ggeffects)

source("../utils/run_lmer_functions.R")
source("../utils/add_network_labels.R")

```



```{r}
# Get and print the current working directory
current_directory <- getwd()
print(current_directory) 
file_path <- paste(current_directory, '../../data/subject_by_node_Viewing1_Viewing2_subs_schaefer_rois.csv', sep = "/")
data = read.csv(file_path)

data$Condition <- as.factor(data$Condition)
condCond_over_Expt<- c(-1,1)
contrasts(data$Condition) <- cbind(condCond_over_Expt) #should be lower in Cont

### Let's drop some motion files    
motion_summary <- read.csv("../../../MadLibs/code/analysis_fmri/_preparing_data/all_subjects_img_trial_motion_summary.csv")

data$Subject <- as.character(data$Subject)
data$img <- as.character(data$stim_file)
motion_summary$Subject <- as.character(motion_summary$sub)
motion_summary$img <- as.character(motion_summary$img)

# Filter only the high motion trials
#high_motion <- subset(motion_summary, high_motion == 'True') #.2
high_motion <- subset(motion_summary, mean_motion > 0.5)

# Create keys for matching
data$key_sub <- paste(data$sub, data$img, sep = "_")
high_motion_keys <- paste(high_motion$sub, high_motion$img, sep = "_")

data$bad <- data$key_sub %in% high_motion_keys
data_clean <- subset(data, bad == FALSE)
data_clean <- data_clean[, !(names(data_clean) %in% c("key_sub", "bad"))]


data <- data_clean


trials_over_threshold <- motion_summary %>%
  group_by(sub) %>%
  dplyr::summarise(n_over_threshold = sum(median_motion > 0.5, na.rm = TRUE))

trials_over_threshold %>%
  ungroup() %>%
  summarise(
    median_n = median(n_over_threshold),
    min_n = min(n_over_threshold),
    max_n = max(n_over_threshold),
    mean_n = mean(n_over_threshold),
    sd_n = sd(n_over_threshold)
  )

trials_over_threshold %>%
  arrange(desc(n_over_threshold)) %>%
  print(n = Inf)


eyetracking_data <-read.csv("/Volumes/FinnLab/datasets/madlibs-eyetracking/results/combined-eye-tracking_behavioral_results_fmri_QCed_screensize_merge_iticorr_mindur100.csv")

eyetracking_subset <- eyetracking_data %>%
  rename(Subject = subject, stim_file = stimulus) %>%
  dplyr::select(Subject, stim_file, mm_direction, mm_position, mm_duration, mm_shape, mm_length, dtw_shift, fixation_map_pearson_r, eyelink_hz, fixation_count_discrepancy)


# Merge datasets
data <- data %>%
  left_join(eyetracking_subset, by = c("Subject", "stim_file"))

```


### set up
```{r}
data <- data %>%
  mutate(
    confidence = confidence / 100,
    self = appraisal_SELF_cond1 / 100,
    other = appraisal_OTHER_cond1 / 100
  )

# Step 3: Create reinterpretation value
data <- data %>%
  mutate(reinterpretation = confidence - self + other)

data$neural_shift <- 1 - atanh(data$R_Value)
data <- data[data$Subject != "sub-016",] #just a terrible tracking subject!!

```



# Edit here to choose the metric!
```{r}
gaze_choice = 'fixation_map_pearson_r'
data$mm_mean5 <- data$fixation_map_pearson_r
data$gaze_change <- 1 - data[[gaze_choice]]


#In the Supplement!
# mm_cols <- c('mm_shape')
# gaze_choice = 'mm_mean5'
# data$mm_mean5 <- data$mm_shape
# data$gaze_change <- 1 - data[[gaze_choice]]


data <- data[data$Condition=='expt',] #just experimental trials


###############################################################################
## GAZE SHIFT SCORE
###############################################################################
# One row per trial (collapse across nodes), drop trials with no shift score,
# then z-score within subject.
gaze_trial_level <- data %>%
  distinct(Subject, stim_file, gaze_change) %>%
  filter(!is.na(gaze_change)) %>%
  group_by(Subject) %>%
  mutate(gaze_z = as.numeric(scale(gaze_change))) %>%
  ungroup() %>%
  dplyr::select(Subject, stim_file, gaze_z)

# Merge the trial-level gaze_z back onto the full node-level data
data <- data %>%
  dplyr::select(-any_of("gaze_z")) %>%
  inner_join(gaze_trial_level, by = c("Subject", "stim_file"))


```


#Adding the network labels!
```{r}

data$semantic_distance <- 1 - data$cosine_sim_avg_inputs_BERT_context_miniLM_L6
data <- data %>%
  filter(!is.na(semantic_distance) & !is.nan(semantic_distance))
data <- data %>%
  filter(!is.na(gaze_z) & !is.nan(gaze_z))

data_experimental <- data[data$Condition=='expt',]
data <- add_schaefer_network_labels(data_experimental)

```


#plotting Fig. 3E
```{r}

node_experimental <- data[data$Node_Number=='1',]

mod_main <- lmer(reinterpretation ~ gaze_z * poly(semantic_distance,3)+  (1+gaze_z|Subject) + (1|stim_file) , data = node_experimental)
tab_model(mod_main)
mod_main <- lmer(reinterpretation ~ gaze_z * semantic_distance+  (1+gaze_z|Subject) + (1|stim_file) , data = node_experimental)


pred <- ggpredict(mod_main, c("gaze_z [-1, 0, 1]", "semantic_distance [.25, .5, .75]"))

p <- ggplot(pred, aes(x = x, y = predicted,
                       group = group, color = group,
                       fill = group, linetype = group)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.15, color = NA) +
  geom_line(linewidth = 1) +
  scale_color_manual(values = c("black", "black", "black")) +
  scale_fill_manual(values = c("black", "black", "black")) +
  scale_linetype_manual(values = c("dotted", "longdash", "solid")) +
  labs(y = NULL, x = NULL)+
  theme_classic() +
  theme(
    aspect.ratio = 1,
    text = element_text(family = "Helvetica Neue"),
    axis.title = element_text(size = 14),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    legend.position = "none",
            panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_blank(),
        panel.border = element_rect(
          colour = "black",
          fill = NA,
          linewidth = 0.5
        ))+
  ylim(0.40, 0.66)

p <- p +
  force_panelsizes(rows = unit(2.5, "in"), cols = unit(2.5, "in"))


ggsave(
  paste0("../../results/eyetracking_plots/neural_gaze_behavioral_model_", gaze_choice, ".png"),
  p, width = 3, height = 3, dpi = 300
)


p

```



#Fig. 4A
```{r}

network = 'DefaultB'
net = data[data$Network_17N==network,]
hist(net$semantic_distance)
hist(net$gaze_change)
net <- net %>%
  filter(!is.na(neural_shift) & !is.na(reinterpretation) & !is.na(semantic_distance))

model3 <- lmerTest::lmer(reinterpretation ~ neural_shift * gaze_z * poly(semantic_distance, 3) + ( 1+gaze_z|Subject) + (1|stim_file) + (1|Node_Number) , data = net, REML=TRUE)
tab_model(model3)

model3 <- lmerTest::lmer(reinterpretation ~ neural_shift * gaze_z * semantic_distance + ( 1+gaze_z|Subject) + (1|stim_file) + (1|Node_Number) , data = net, REML=TRUE)

print(summary(model3))


# Test the slope of neural_shift at specific values of gaze_z and semantic_distance
slopes(model3,
  variables = "neural_shift",
  newdata = datagrid(
    gaze_z            = c(-1, 0, 1),  #  low/mid/high gaze values
    semantic_distance = c(0.25, 0.50, 0.75)  # 
  )
)

hypotheses(slopes(model3,
  variables = "neural_shift",
  newdata = datagrid(
    gaze_z = c(-1, 1),
    semantic_distance = 0.75
  )),
  hypothesis = "b1 = b2"
)


pred <- ggpredict(model3, c("neural_shift", "gaze_z [-1,0,1]", "semantic_distance [0.25, 0.50, 0.75]"))


p <- ggplot(pred, aes(x = x, y = predicted, 
                      group = group, color = group, 
                      fill = group, linetype = group)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.15, color = NA) +
  geom_line(size = .75) +
  facet_wrap(~ facet, labeller = label_both) +  # 'facet' is the third variable in ggpredict output
  scale_color_manual(values = c("#dc2e2c", "#dc2e2c", "#dc2e2c")) +
  scale_fill_manual(values = c("#dc2e2c", "#dc2e2c", "#dc2e2c")) +
  scale_linetype_manual(values = c("dotted", "longdash", "solid")) +
  labs(y = "reinterpretation (pred.)", x = "neural shift", title = network) +
  theme_classic() +
  theme(
    aspect.ratio = 1,
    text = element_text(family = "Helvetica Neue"),
    axis.title = element_text(size = 14),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    legend.position = "none",
            panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_blank(),
        panel.border = element_rect(
          colour = "black",
          fill = NA,
          linewidth = 0.5
        ))
p


p 

ggsave(
  paste0(
    "../../results/eyetracking_plots/",
    "reinterpretation_reinterpretation_by_neural_gaze_semantic_distance_",
    network, "_",
    gaze_choice,
    ".png"
  ),
  p,
  width = 9,
  height = 3,
  dpi = 300
)

pred_high <- subset(pred, facet == "0.75")

p_high <- ggplot(
  pred_high,
  aes(
    x = x,
    y = predicted,
    group = group,
    color = group,
    fill = group,
    linetype = group
  )
) +
  geom_ribbon(
    aes(ymin = conf.low, ymax = conf.high),
    alpha = 0.15,
    color = NA
  ) +
  geom_line(size = .75) +
  scale_color_manual(values = c("#dc2e2c", "#dc2e2c", "#dc2e2c")) +
  scale_fill_manual(values = c("#dc2e2c", "#dc2e2c", "#dc2e2c")) +
  scale_linetype_manual(values = c("dotted", "longdash", "solid")) +
  labs(
    y = NULL,
    x = NULL,
  ) +
  theme_classic() +
  theme(
    aspect.ratio = 1,
    text = element_text(family = "Helvetica Neue"),
    axis.title = element_text(size = 14),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    legend.position = "none",
            panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_blank(),
        panel.border = element_rect(
          colour = "black",
          fill = NA,
          linewidth = 0.5
        ))+
  ylim(0.1, 1)
p_high
p_high <- p_high +
  force_panelsizes(rows = unit(2.5, "in"), cols = unit(2.5, "in"))

ggsave(
  paste0(
    "../../results/eyetracking_plots/",
    "reinterpretation_reinterpretation_by_neural_gaze_semantic_distance_HIGH_",
    network, "_",
    gaze_choice,
    ".png"
  ),
  p_high,
  width = 3,
  height = 3,
  dpi = 300
)



```


# BOTH VISUAL NETWORKS COMBINED -- this is what is in the main manuscript! Change to be VisPeri or VisCent for the Supplement
#Fig. 4B
```{r}
network = 'both_visual'


net <- data[data$Network_17N %in% c("VisPeri", "VisCent"), ]


model3 <- lmerTest::lmer(reinterpretation ~ neural_shift * gaze_z * poly(semantic_distance, 3) + ( 1 +gaze_z|Subject) + (1|stim_file) + (1|Node_Number) , data = net)
tab_model(model3)

model3 <- lmerTest::lmer(reinterpretation ~ neural_shift * gaze_z * semantic_distance + ( 1+gaze_z|Subject) + (1|stim_file) + (1|Node_Number) , data = net)
tab_model(model3)


print(summary(model3))


library(ggeffects)
pred <- ggpredict(model3, c("neural_shift","gaze_z [-1,0,1]","semantic_distance [0.25, 0.50, 0.75]"))

pred <- ggpredict(model3, c("neural_shift", "gaze_z [-1, 0, 1]", "semantic_distance [0.25, 0.50, 0.75]"))

p <- ggplot(pred, aes(x = x, y = predicted, 
                      group = group, color = group, 
                      fill = group, linetype = group)) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.15, color = NA) +
  geom_line(size = .75) +
  facet_wrap(~ facet, labeller = label_both) +  
  scale_color_manual(values =  c("#744083", "#744083", "#744083")) +
  scale_fill_manual(values =  c("#744083", "#744083", "#744083")) +
  scale_linetype_manual(values = c("dotted", "longdash", "solid")) +
  labs(y = "reinterpretation (pred.)", x = "neural shift", title = network) +
  theme_classic() +
  theme(
    aspect.ratio = 1,
    text = element_text(family = "Helvetica Neue"),
    axis.title = element_text(size = 14),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    legend.position = "none",
            panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_blank(),
        panel.border = element_rect(
          colour = "black",
          fill = NA,
          linewidth = 0.5
        ))
p


p 
ggsave(
  paste0(
    "../../results/eyetracking_plots/",
    "reinterpretation_reinterpretation_by_neural_gaze_semantic_distance_",
    network, "_",
    gaze_choice,
    ".png"
  ),
  p,
  width = 9,
  height = 3,
  dpi = 300
)



pred_high <- subset(pred, facet == "0.75")

p_high <- ggplot(
  pred_high,
  aes(
    x = x,
    y = predicted,
    group = group,
    color = group,
    fill = group,
    linetype = group
  )
) +
  geom_ribbon(
    aes(ymin = conf.low, ymax = conf.high),
    alpha = 0.15,
    color = NA
  ) +
  geom_line(size = .75) +
  scale_color_manual(values =  c("#744083", "#744083", "#744083")) +
  scale_fill_manual(values =  c("#744083", "#744083", "#744083")) +
  scale_linetype_manual(values = c("dotted", "longdash", "solid")) +
  labs(
    y = NULL,
    x = NULL,
    #title = paste(network, "- High Semantic Distance")
  ) +
  theme_classic() +
  theme(
    aspect.ratio = 1,
    text = element_text(family = "Helvetica Neue"),
    axis.title = element_text(size = 14),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    legend.position = "none",
            panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_blank(),
        panel.border = element_rect(
          colour = "black",
          fill = NA,
          linewidth = 0.5
        ))+
  ylim(0.1, 1)
p_high <- p_high +
  force_panelsizes(rows = unit(2.5, "in"), cols = unit(2.5, "in"))
p_high

ggsave(
  paste0(
    "../../results/eyetracking_plots/",
    "reinterpretation_reinterpretation_by_neural_gaze_semantic_distance_HIGH_",
    network, "_",
    gaze_choice,
    ".png"
  ),
  p_high,
  width = 3,
  height = 3,
  dpi = 300
)


model3 <- lmerTest::lmer(reinterpretation ~ neural_shift * gaze_z * semantic_distance + ( 1+gaze_z|Subject) + (1|stim_file) + (1|Node_Number) , data = net)
tab_model(model3)


slopes(model3,
  variables = "neural_shift",
  newdata = datagrid(
    gaze_z            = c(-1, 0, 1),  # low/mid/high gaze values
    semantic_distance = c(0.25, 0.50, 0.75)  #three facets
  )
)

hypotheses(slopes(model3,
  variables = "neural_shift",
  newdata = datagrid(
    gaze_z = c(-1, 1),
    semantic_distance = 0.75
  )),
  hypothesis = "b1 = b2"
)


```


# Fig. 4C
```{r}
data_sub <- data %>%
  filter(Network_17N %in% c("VisPeri", "VisCent", "DefaultB")) %>%
  filter(
    !is.na(neural_shift) &
    !is.na(reinterpretation) &
    !is.na(semantic_distance) &
    !is.na(gaze_z)
  ) %>%
  mutate(
    Network_17N = case_when(
      Network_17N %in% c("VisPeri", "VisCent") ~ "Visual",
      Network_17N == "DefaultB" ~ "DefaultB"
    ),
    Network_17N = factor(Network_17N, levels = c("DefaultB", "Visual"))
  )

model_combined <- lmerTest::lmer(
  reinterpretation ~ neural_shift * gaze_z * poly(semantic_distance, 3) * Network_17N +
    (1 + gaze_z| Subject) + (1 | stim_file) + (1 | Node_Number),
  data = data_sub
)

model_combined <- lmerTest::lmer(
  reinterpretation ~ neural_shift * gaze_z * semantic_distance * Network_17N +
    (1 + gaze_z| Subject) + (1 | stim_file) + (1 | Node_Number),
  data = data_sub
)

slopes_high <- slopes(
  model_combined,
  variables = "neural_shift",
  newdata = datagrid(
    gaze_z = c(-1, 0, 1),
    semantic_distance = 0.75,
    Network_17N = c("DefaultB", "Visual")
  )
) %>%
  as.data.frame() %>%
  mutate(
    gaze_label = factor(
      gaze_z,
      levels = c(-1, 0, 1),
      labels = c("-1", "0", "1")
    ),
    Network_17N = factor(
      Network_17N,
      levels = c("DefaultB", "Visual"),
      labels = c("DMN-B", "Visual")
    )
  )



p_slopes <- ggplot(slopes_high, aes(x = gaze_label, y = estimate,
                                      color = Network_17N, group = Network_17N)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey70") +
  geom_line(position = position_dodge(width = 0.3), linewidth = 0.75) +
  # geom_pointrange(aes(ymin = conf.low, ymax = conf.high),
  #                  position = position_dodge(width = 0.3), size = 0.6) +
  geom_pointrange(aes(ymin = estimate - std.error, ymax = estimate + std.error),
                   position = position_dodge(width = 0.3), size = 0.6) +
scale_color_manual(
  values = c(
    "DMN-B" = "#dc2e2c",
    "Visual" = "#744083"
  )
)+labs(
    x = NULL,
    y = NULL,
    color = NULL,
  ) +
  theme_classic() +
  theme(
    aspect.ratio = 1,
    text = element_text(family = "Helvetica Neue"),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    legend.position = "none",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_blank(),
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.5)
  )+
  ylim(-.1,.2)

p_slopes
p_slopes <- p_slopes +
  force_panelsizes(rows = unit(2.5, "in"), cols = unit(2.5, "in"))



ggsave(
  paste0(
    "../../results/eyetracking_plots/",
    "reinterpretation_slopes_plot",
    network, "_",
    gaze_choice,
    ".png"
  ),
  p_slopes,
  width = 3,
  height = 3,
  dpi = 300
)

```

# doing the statistical comparison  for the plot above
```{r}

data_sub <- data %>%
  filter(Network_17N %in% c("VisPeri", "VisCent", "DefaultB")) %>%
  filter(
    !is.na(neural_shift) &
    !is.na(reinterpretation) &
    !is.na(semantic_distance) &
    !is.na(gaze_z)
  ) %>%
  mutate(
    Network_17N = case_when(
      Network_17N %in% c("VisPeri", "VisCent") ~ "Visual",
      Network_17N == "DefaultB" ~ "DefaultB"
    ),
    Network_17N = factor(
      Network_17N,
      levels = c("DefaultB", "Visual")
    )
  )

model_combined <- lmerTest::lmer(
  reinterpretation ~
    neural_shift * gaze_z * semantic_distance * Network_17N +
    (1 + gaze_z | Subject) +
    (1 | stim_file) +
    (1 | Node_Number),
  data = data_sub
)

tab_model(model_combined)

## --- Network-specific slopes at HIGH semantic distance ----------
slopes_high <- slopes(
  model_combined,
  variables = "neural_shift",
  newdata = datagrid(
    gaze_z = c(-1, 0, 1),
    semantic_distance = 0.75,
    Network_17N = c("DefaultB", "Visual")
  )
)

slopes_high

## --- Formal DefaultB vs Visual test at HIGH semantic distance ----
gaze_levels <- c(-1, 0, 1)

network_diff_high <- purrr::map_dfr(gaze_levels, function(gz) {

  test <- hypotheses(
    slopes(
      model_combined,
      variables = "neural_shift",
      newdata = datagrid(
        gaze_z = gz,
        semantic_distance = 0.75,
        Network_17N = c("DefaultB", "Visual")
      )
    ),
    hypothesis = "b1 = b2"
  )

  test$gaze_z <- gz
  test
})

network_diff_high


```


#Fig 4D -- Are DMN-B and combined Visual-network reinterpretation signals independent of one another?
```{r}

## aggregate data 

data_clean <- data %>%  #these should be out 
  filter(
    !is.na(neural_shift),
    !is.na(reinterpretation),
    !is.na(semantic_distance),
    !is.na(gaze_z)
  )


df_agg <- data_clean %>%
  filter(Network_17N %in% c("VisPeri", "VisCent", "DefaultB")) %>%
  
  # Combine VisPeri and VisCent into one Visual network
  mutate(
    Network_17N = case_when(
      Network_17N %in% c("VisPeri", "VisCent") ~ "Visual",
      Network_17N == "DefaultB"                ~ "DefaultB"
    )
  ) %>%
  
  # Average neural shift within Subject × stimulus × network
  group_by(Subject, stim_file, Network_17N) %>%
  summarise(
    neural_shift      = mean(neural_shift, na.rm = TRUE),
    semantic_distance = first(semantic_distance),
    reinterpretation  = first(reinterpretation),
    gaze_z            = first(gaze_z),
    .groups = "drop"
  )


## 1. Long-format model

df_agg <- df_agg %>%
  mutate(
    Network_17N = factor(
      Network_17N,
      levels = c("DefaultB", "Visual")
    )
  )


m_long <- lmer(
  reinterpretation ~ neural_shift * semantic_distance * Network_17N +
    (1 +gaze_z| Subject) +
    (1 | stim_file),
  data = df_agg,
  REML = FALSE
)

summary(m_long)


## 2. Wide format: each network as its own predictor ────────────────────────
## Creates:
##   DefaultB_ns = mean DMN-B neural shift
##   Visual_ns   = mean neural shift across VisPeri + VisCent
df_wide <- df_agg %>%
  pivot_wider(
    names_from  = Network_17N,
    values_from = neural_shift,
    names_glue  = "{Network_17N}_ns"
  ) %>%
  filter(
    complete.cases(
      DefaultB_ns,
      Visual_ns,
      reinterpretation,
      semantic_distance,
      gaze_z
    )
  )

```

```{r}

SD_HI <- 0.75
GZ_HI <- 1

## Models 

# DMN-B unadjusted
a <- lmer(
  reinterpretation ~
    DefaultB_ns * semantic_distance +
    (1 +gaze_z| Subject) +
    (1 | stim_file),
  data = df_wide,
  REML = FALSE
)


# Combined Visual network unadjusted
c <- lmer(
  reinterpretation ~
    Visual_ns * semantic_distance * gaze_z +
    (1 + gaze_z | Subject) +
    (1 | stim_file),
  data = df_wide,
  REML = FALSE
)


# Joint model: DMN-B + Visual
b <- lmer(
  reinterpretation ~
    DefaultB_ns * semantic_distance +
    Visual_ns * semantic_distance * gaze_z +
    (1 + gaze_z | Subject) +
    (1 | stim_file),
  data = df_wide,
  REML = FALSE
)


##  Model tables 

tab_model(
  a,
  b,
  dv.labels = c(
    "DMN-B unadjusted",
    "Both (DMN-B adjusted)"
  )
)

tab_model(
  c,
  b,
  dv.labels = c(
    "Visual unadjusted",
    "Both (Visual adjusted)"
  )
)


##  1. Marginal slopes 

get_slope <- function(model, focal, network, adj, needs_gaze = TRUE) {

  grid <- if (needs_gaze) {

    datagrid(
      model = model,
      semantic_distance = SD_HI,
      gaze_z = GZ_HI
    )

  } else {

    datagrid(
      model = model,
      semantic_distance = SD_HI
    )

  }

  slopes(
    model,
    variables = focal,
    newdata = grid,
    re.form = NA
  ) %>%
    as.data.frame() %>%
    transmute(
      network,
      model = adj,
      estimate,
      se = std.error,
      p = p.value,
      conf.low,
      conf.high
    )
}


df_plot <- bind_rows(

  get_slope(
    a,
    "DefaultB_ns",
    "DMN-B",
    "Unadjusted",
    needs_gaze = FALSE
  ),

  get_slope(
    b,
    "DefaultB_ns",
    "DMN-B",
    "Adjusted"
  ),

  get_slope(
    c,
    "Visual_ns",
    "Visual",
    "Unadjusted"
  ),

  get_slope(
    b,
    "Visual_ns",
    "Visual",
    "Adjusted"
  )

) %>%
  mutate(

    network = factor(
      network,
      levels = c("DMN-B", "Visual")
    ),

    model = factor(
      model,
      levels = c("Unadjusted", "Adjusted")
    ),

    fill_group = factor(
      paste0(network, "_", model),
      levels = c(
        "DMN-B_Unadjusted",
        "DMN-B_Adjusted",
        "Visual_Unadjusted",
        "Visual_Adjusted"
      )
    )
  )


## Print marginal slopes 

cat(
  "=== slope of reinterpretation on neural shift, semantic distance =",
  SD_HI,
  "(Visual also at gaze_z =",
  GZ_HI,
  ") ===\n"
)


df_plot %>%
  transmute(
    network,
    model,
    slope = round(estimate, 3),
    SE = round(se, 3),
    p = signif(p, 3),
    CI = paste0(
      "[",
      round(conf.low, 3),
      ", ",
      round(conf.high, 3),
      "]"
    )
  ) %>%
  as.data.frame() %>%
  print(row.names = FALSE)


## Percent attenuation: unadjusted → adjusted 

cat("\n=== % attenuation, unadjusted -> adjusted ===\n")


df_plot %>%
  dplyr::select(
    network,
    model,
    estimate
  ) %>%
  pivot_wider(
    names_from = model,
    values_from = estimate
  ) %>%
  mutate(
    pct_attenuation = round(
      100 * (1 - Adjusted / Unadjusted),
      1
    )
  ) %>%
  as.data.frame() %>%
  print(row.names = FALSE)




## Plot 
## Solid bars  = unadjusted
## Striped bars = adjusted for the other network


fill_vals <- c(
  "DMN-B_Unadjusted"  = "#dc2e2c",
  "DMN-B_Adjusted"    = "#dc2e2c",
  "Visual_Unadjusted" = "#744083",
  "Visual_Adjusted"   = "#744083"
)


pattern_vals <- c(
  "DMN-B_Unadjusted"  = "none",
  "DMN-B_Adjusted"    = "stripe",
  "Visual_Unadjusted" = "none",
  "Visual_Adjusted"   = "stripe"
)


figure <- ggplot(
  df_plot,
  aes(
    x = network,
    y = estimate,
    fill = fill_group,
    colour = fill_group,
    pattern = fill_group
  )
) +

  geom_col_pattern(
    position = position_dodge(width = 0.6),
    width = 0.5,
    alpha = 0.7,
    linewidth = 1.2,
    pattern_fill = "white",
    pattern_colour = "white",
    pattern_spacing = 0.06,
    pattern_density = 0.3
  ) +

  geom_errorbar(
    aes(
      ymin = estimate - se,
      ymax = estimate + se
    ),
    position = position_dodge(width = 0.6),
    width = 0.15,
    linewidth = 0.65,
    colour = "grey30"
  ) +

  geom_hline(
    yintercept = 0,
    linewidth = 0.4,
    colour = "grey40"
  ) +

  scale_fill_manual(
    values = fill_vals
  ) +

  scale_colour_manual(
    values = fill_vals,
    guide = "none"
  ) +

  scale_pattern_manual(
    values = pattern_vals,
    guide = "none"
  ) +

  labs(
    x = NULL,
    y = NULL
  ) +

  theme_classic() +

  theme(
    aspect.ratio = 1,
    legend.position = "none",
    text = element_text(
      family = "Helvetica Neue"
    ),
    axis.title = element_text(
      size = 14
    ),
    axis.text.x = element_text(
      size = 12
    ),
    axis.text.y = element_text(
      size = 12
    ),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_blank(),
    panel.border = element_rect(
      colour = "black",
      fill = NA,
      linewidth = 0.5
    )
  ) +

  ylim(-0.1, 0.3)


figure <- figure +
  force_panelsizes(
    rows = unit(2.5, "in"),
    cols = unit(2.5, "in")
  )


figure


ggsave(
  paste0(
    "../../results/eyetracking_plots/",
    "dmnb_stability_both_Visual_",
    gaze_choice,
    ".png"
  ),
  figure,
  width = 3.4,
  height = 3,
  dpi = 300
)
```
